%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Xun (Neal) Yu}{}

\address{Fremont, CA}

\mobile{+1 979-703-9128}
\email{\href{mailto:neal.yu07@gmail.com}{\nolinkurl{neal.yu07@gmail.com}}}
\github{nealxun}
\linkedin{findnealyu}
\twitter{nealxun1}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {June, 2022}
    {Xun (Neal) Yu~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{professional-experience}{%
\section{PROFESSIONAL EXPERIENCE}\label{professional-experience}}

\begin{cventries}
    \cventry{Forecasting Analyst}{Apple, AppleCare}{Sunnyvale, CA}{01/2020 - Present}{\begin{cvitems}
\item In charge of contact center demand forecasting in the EMEA market for 24 languages and more than 100 queues.
\item Rebuilt baseline forecast model to take COVID impact into consideration via simulating the additional regressor (such as a shock variable) to model the impact of different waves of COVID. Also introduced the idea of classification before forecasting so that different language queues can be assigned to different customized models. Together achieved a 5\% accuracy gain and 50\% model running time reduction.
\item Enhanced tier 2 queues prediction model via introducing a brand new adaptive smoothing model as well as a dynamic model selection procedure, resulting in a 4\% accuracy improvement.
\end{cvitems}}
    \cventry{Statistician}{Tesla, Service Demand Planning}{Fremont, CA}{09/2017 - 12/2019}{\begin{cvitems}
\item Created and delivered baseline statistical forecasts for all service parts and accessories (12,000+ SKU) from scratch, applied multiple algorithms including ETS, ARIMA, and dynamic regression that achieved 80\% overall forecast accuracy.
\item Highly shaped optimization skills via designing an integer programming tool to assign various parts to different demand planning managers to achieve balance and diversify the risk.
\end{cvitems}}
    \cventry{Business Analyst}{Spotlight Energy}{Houston, TX}{08/2016 – 09/2017}{\begin{cvitems}
\item Highly improved web scraping skills via developing a python web crawler to automatically retrieve pipeline EBB and trading data for daily report building.
\item Invented a trading optimization model to automatically calculate the value of hundreds of natural gas shipping paths, based on spread, cut percentage, as well as existing capacity, resulting in more than 500K profit.
\end{cvitems}}
    \cventry{Research Intern}{Texas A\&M University, College of Education}{College Station, TX}{05/2016 – 08/2016}{\begin{cvitems}
\item Successfully applied Hidden Markov Model in predicting the student's likelihood of mastering a certain skill based on his/her response sequence, providing a key component for a prototype of the adaptive online course.
\item Innovated a neural network based model to detect whether the student is “wheel spinning” on a certain skill, increasing the recall rate by 10\% and precision rate by 50\%.
\end{cvitems}}
\end{cventries}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{Master of Science, Industrial Engineering}{Texas A\&M University}{College Station, TX}{2014 - 2016}{\begin{cvitems}
\item GPA: 3.91; Passed CFA Level I Exam; SAS Base Certificate; Business Management Certificate
\end{cvitems}}
    \cventry{Bachelor of Science, Industrial Engineering}{North Dakota State University}{Frago, ND}{2010 - 2013}{\begin{cvitems}
\item GPA: 3.80; IIE Six Sigma Green Belt; Passed FE (Fundamentals Engineering) Exam
\end{cvitems}}
\end{cventries}

\hypertarget{project}{%
\section{PROJECT}\label{project}}

\begin{cventries}
    \cventry{Paper Helicopter Design Competition}{}{}{03/2016 – 05/2016}{\begin{cvitems}
\item Achieved 50\% fly time increment in implementing advanced response surface and robust design method to identify the optimized value for each variable such as wing length, wing width, and body length.
\end{cvitems}}
    \cventry{Social Network Analysis within Movies }{}{}{05/2015 – 08/2015}{\begin{cvitems}
\item Strongly improved programming skills via designing algorithms to find certain structures of movie social networks. The objective is to find if there is any relationship between movie graph structure and ratings.
\end{cvitems}}
\end{cventries}

\hypertarget{skill-and-language}{%
\section{SKILL AND LANGUAGE}\label{skill-and-language}}

\begin{cventries}
    \cventry{Skills: R, Python, SQL, Tableau, SAS, VBA, Power BI, Advanced Excel}{}{}{}{}\vspace{-4.0mm}
    \cventry{Languages: Mandarin Chinese (native), English (with work proficiency)}{}{}{}{}\vspace{-4.0mm}
\end{cventries}



\end{document}
